GSEA datasets for FDR benchmarking

### 2017-12-09 datasets/GSEA/gsea.Rmd
Generalized plotCovariateBoxplot for any SB object

rank_scatter( dat=goRes, pval="over_represented_pvalue", 
              covariate="numInCat", bins=50, funx=log2, 
              funfill=log10_trans()) +
    ylim(0, 12) + ggtitle("Over-represented gene sets") +
    xlab( expression(log[10]~"(# of genes)")) +
    ylab( expression(-log[10]~"(p-value)") ) 
```

@@

under_represented_pvalue
dplyr:::filter( goRes, numDEInCat > 0, numInCat > 10 ) %>%
  strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=10)

@@

set1 <- getOverlapIndexes( c("lfdr","ihw-a10","bl-df03","qvalue","bh", "bonf"), alpha=0.1, sGSEA=sGSEAMouse)
set2 <- getOverlapIndexes( c("lfdr", "ihw-a10"), alpha=0.1, sGSEA=sGSEAMouse )
set3 <- getOverlapIndexes( c("bl-df03"), alpha=0.1, sGSEA=sGSEAMouse )

sizesDf <- data.frame( 
  size=c( rowData( sGSEAMouse )$ind_covariate[which(set1)], 
          rowData( sGSEAMouse )$ind_covariate[which(set2)], 
          rowData( sGSEAMouse )$ind_covariate[which(set3)] ),
  label=rep(c("set1", "set2", "set3"), c(sum(set1), sum(set2), sum(set3)) ) )

ggplot( sizesDf, aes( label, log2(size) )) +
  geom_boxplot()

>>>>

@@

dplyr:::filter( goRes, numDEInCat > 0, numInCat > 10 ) %>%
  strat_hist( pval="over_represented_pvalue", covariate="numInCat", maxy=10)

@@

plotCovariateBoxplots( sGSEAMouse, alpha=0.1, nsets=4, methods=methods, trans=log2, maxNum=5)

plotCovariateBoxplots( sGSEA, alpha=0.1, nsets=7, methods=methods, trans=log2, maxNum=5)
